Fifteen years of decentralization attempts

### 2014-03-24 paper.tex
second round of typo fixes

	Decentralizing systems comes with a variety of problems. The most important reasons why one would decentralize are security and anonymity. When having a central authority this authority can be used for bootstrapping, key management and to manage the reputation of the users, but if one of these authorities were taken control of, security of the anonymity could be compromised. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor.

>>>>

	Decentralizing systems comes with a variety of problems. The most important reasons why one would decentralize are security and anonymity. When having a central authority, this authority can be used for bootstrapping, key management and to manage the reputation of the users. If one of these authorities were taken control of, security of the anonymity could be compromised. When removing this central authority, these components needs to be spread across the peers in the network. In this section we will explain the various problems that are involved when decentralizing Tor.
